### 2025-10-06 Scripts/Manuscript/manuscript.Rmd
Rewrites

classoption       : man
output            : papaja::apa6_pdf
knit              : worcs::cite_all
---

```{r setup, include = FALSE}
# loading R libraries
library(papaja)
library(worcs)
library(lavaan)
library(psych)
library(metafor)
library(forcats)
library(ggplot2)
library(grid)

@@

\renewcommand{\arraystretch}{0.7} <!-- reducing the line spacing within tables -->

\renewcommand{\topfraction}{.8} <!-- max fraction of page for floats at top -->

\renewcommand{\bottomfraction}{.8} <!-- max fraction of page for floats at bottom -->

\renewcommand{\textfraction}{.15} <!-- min fraction of page for text -->

\renewcommand{\floatpagefraction}{.8} <!-- min fraction of page that should have floats .66 -->

@@

The challenge with measurement in quantitative psychological research is that unlike height or weight, psychological constructs cannot be directly measured. Instead we use scores from a measurement as a proxy indicator for that psychological construct. However, we cannot simply assume that any measure we create will form a good indicator of the construct. We have to substantiate this. Psychometrics can be used to statistically estimate the measure's validity, still validating a measure entails a substantial research effort. Regardless, the burden of validating a measure – besides some well-established psychiatric and personality measures – is most often placed on the researcher conducting a study of a psychological phenomenon. When the effort involved in validating a measure is relegated to be only a component of a study, then how well does the measurement validation process go?

## Measurement Validation
When validating a measure of a psychological construct, two main psychometric components are of interest: construct validity & reliability. Construct validity refers to whether the variance in the measured item scores between participants can be attributed to variance in unobserved constructs between participants [@cronbachConstructValidityPsychological1955; @vazireCredibilityReplicabilityImproving2022]. Reliability refers to how consistent a participant's responses on a measurement are [@nunnallyOverviewPsychologicalMeasurement1978; @mellenberghConceptualIntroductionPsychometrics2011]. Reliability is part of the validation of a measure because a measure that does not consistently capture a participant's response, cannot accurately capture a construct [@crutzenScaleQualityAlpha2017b]. As an example, suppose we have a measure and we want it to measure general intelligence, and we want to validate this as a measure of general intelligence. We would see our measurement as construct valid if being more intelligent resulted in generally scoring higher on our test, and our measurement would be reliable if the score of people on our measure consistently reflected their actual intelligence.

In practice construct validity is often evaluated through factor analysis. In factor analysis, a model is fitted to explain as much of the variance of multiple items through a smaller number of factors, or weighted averages of the item scores. To fit a factor model, the number of factors are first specified, and then the fit of that model on the data can be evaluated. Preferably, a model with the number of factors corresponding to the number of constructs of interest should show adequate fit on the data. Additionally, the items aimed at the same construct should be statistically related to the same factor. For example, suppose items 1 through 5 from our general intelligence measure are meant to capture verbal intelligence, and items 6 through 10 are distinctly about mathematical intelligence. To establish construct validity, we want to find that a two factor model on our intelligence measure to show adequate fit, with one factor to which only items 1 through 5 relate strongly, and one to which only items 6 through 10 relate strongly. However, even in this ideal scenario, the factor relations may not be stable for this measure in other contexts and implementations, a concept known as measurement invariance [@hornPracticalTheoreticalGuide1992; @cheungDirectComparisonApproach2012].

Reliability gives us an indication of how much our measure captures the signal of our measured variables over noise. Psychometrics offers various ways to assess reliability empirically [@nunnallyOverviewPsychologicalMeasurement1978; @mellenberghConceptualIntroductionPsychometrics2011]. For example, we can compare scores on multiple equivalent forms of the test, between multiple different raters, or between multiple different timepoints of the same test. Still, the most common way to assess reliability for single measurement instances is through internal consistency indicators. The most common internal consistency indicator is the Cronbach's Alpha coefficient. The Cronbach's Alpha coefficient is defined as “the average of all the possible split-half coefficients for a given test” [@cronbachCoefficientAlphaInternal1951]. Here split-half coefficients being the correlation between two halves of the same test. It can be calculated by taking the ratio of interitem covariance to total variance and multiplying it by n / (n - 1), where n is the number of items in the scale. However, Cronbach's Alpha comes with strong assumptions on the underlying factor structure, including that the measure is unidimensional, so a single factor. Furthermore, because Cronbach's alpha is proportional to the total variance in the target variable in the sample, it is an indicator of reliability within a particular sample and not of the reliability of the measure in general. Despite this many researchers report and interpret Cronbach's Alpha as a universal quality of the measure [@cortinaWhatCoefficientAlpha1993; @schmittUsesAbusesCoefficient1996].

Thus, psychometric tests are useful but they have their limitations. Even simple factor analyses - unless the amount of variance explained by the factors is large and the factor structure is clear - require sample sizes of at least 100 [@maccallumSampleSizeFactor1999; @gorsuchFactorAnalysis2013]. Furthermore, even in the latter case factor analysis may not converge with small sample sizes. If we want to know the reliability and validity of not just one measurement but for the measure across multiple contexts, we need to conduct multiple studies. Additionally, larger sample sizes per relevant group to detect meaningful effects when checking for measurement invariance across groups [@meadePowerPrecisionConfirmatory2007; @frenchMeasurementInvarianceTechniques2016; @koziolImpactModelParameterization2018]. However, what we observe in the literature is that most measures are reused once or never [@elsonPsychologicalMeasuresArent2023; @anvariFragmentedFieldConstruct2025; @anvariDefragmentingPsychology2025], let alone that they are systematically tested on reliability and validity. @maireadshawMeasurementPracticesLargescale2020 checked the factor structure and reliability of measures used in the Many Labs 2 replication project [@kleinManyLabs22018b] on the available data. They observed that for the scales they assessed, no factor model fit congruent with the use of the scales met all of their evaluation criteria. Furthermore, the overall sample Cronbach's alpha level of all scales was below .5, a level of reliability far below what many would consider acceptable for almost all research purposes.

@@

As illustrated in the previous section, validating measurement is a complex but essential part of doing psychological research. Yet the scientific community has not fully stepped up to this challenge [@flakeMeasurementSchmeasurementQuestionable2020]. A large number of measures used in the psychological literature lack information on the validity and reliability of the measure [@hoganEmpiricalStudyReporting2004; @flakeConstructValidationSocial2017; @flakeConstructValidityValidity2022].

Questionable Measurement Practices (QMPs) are practices that raise doubts about a measurement’s validity [@flakeMeasurementSchmeasurementQuestionable2020] and have been coined as a term analogous to Questionable Research Practices [QRPs; @simmonsFalsePositivePsychologyUndisclosed2011a; @johnMeasuringPrevalenceQuestionable2012a; @wichertsDegreesFreedomPlanning2016a]. QMPs range from lack of transparency in the reporting of the measure and unclear motivation in choice of measure to poor justification for modifications of a measure and procedure of an existing measure [@flakeMeasurementSchmeasurementQuestionable2020]. @flakeConstructValidityValidity2022 documented QMPs among 100 replications and their respective original articles from the Reproduciblity Project Psychology [@opensciencecollaborationEstimatingReproducibilityPsychological2015]. They coded the number of measures, the number of items in the measure, and the information that was reported describing the measure and justifying its use. They observed limited reporting of evidence demonstrating the reliability and validity of the measurement. Additionally, only eight of the 40 translated scales contained validity evidence for the translated version. Furthermore, reporting of reliability may not only be little, but also biased. @husseyAberrantAbundanceCronbachs2023 observed a disproportional amount of Cronbach's Alpha values at the common acceptably reliable threshold value of .70, and low reporting just below .70. Thus the lack of reported measurement evidence may on occasion be hiding psychometric skeletons in the closet.

Further findings by @flakeConstructValidityValidity2022 and others [@flakeConstructValidationSocial2017; @maireadshawMeasurementPracticesLargescale2020] also show that QMPs not only limit the reported validity of that measurement. The lack of information also creates challenges for replicating researchers. Basic content descriptions such as the number of items, the response format, and the scoring of the scale were irregular (!!!exact numbers!!!). If it is not clear what items were used, how they were scored, and how they were administered, then it is challenging to reconstruct the measurement for a replication study. In turn, the replication may assess the constructs in a substantially different way, or even assess different constructs. If different constructs are assessed, the replication cannot be seen as a test of the same phenomenon as the original. On the other hand, if the same constructs are assessed very differently, the estimated effects in the replication cannot easily be substantially compared to the effects in the original study. In either case, substantial comparisons between original and replication are hindered.

## Research Aim

Our aim is to provide a descriptive account of the reliability, validity, and reporting practices of measurement in replications and related original research. We coded several measurement reporting practices in replications and original articles. Additionally, we estimated reliability and validity from openly available replication data on item responses. This replication data was available across multiple labs. Our unique contribution is based on the combination of reported and the recalculated measurement information. These two sources combined allows us to capture a "double whammy" scenario where there is uncertainty in the reliability and validity of these measures when we calculate these ourselves, and where QMPs obscure the ability to evaluate the measure as well as inhibiting future researchers to recreate the measurement and validate it in a new study. Besides this, our study also functions as a conceptual replication of existing research on reporting practices and measurement validation, by assessing measurement reporting differently and using a novel set of replications and original research. While theoretical considerations are  key for evaluating how the content of the measure fits to the constructs of interest, we do not look into these here. Evaluating the theory of a measurement requires domain specific knowledge for each measure which is outside of this article's scope. We refer interested readers to articles discussing theory in measurement elsewhere [e.g.; @gehlbachMeasureTwiceCut2011; @humphryPsychologicalMeasurementTheory2017; @borgstedeMeaningfulMeasurementRequires2023; @hasselmanGoingSquaresTheorybased2023].

@@

## Preregistration
We preregistered data collection, coding protocol, and planned analyses: <https://osf.io/jgxyu>. We deviated from our coding protocol as is explained further in the text. Our pre-registered analyses have been move to the [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_exploratory_version_pre-reg_analyses.Rmd) in favor of focusing on the descriptive results.

## Data, Materials, and Online Resources
TThis manuscript was created in RStudio [*v`r rstudioapi::versionInfo()$version`*\; @R-Rstudio] with R Version `r paste0(R.Version()$major, ".", R.Version()$minor)` [@R-base], and generated using the Workflow for Open Reproducible Code in Science [*v`r getNamespaceVersion("worcs")[[1]]`*\; @R-worcs] to ensure reproducibility and transparency. All code and data used to generate this manuscript and its results are available at: <https://github.com/CasGoos/measurement_and_replication> and <https://osf.io/9r8yt/> (DOI: 10.17605/OSF.IO/9R8YT).

## Reporting
We report how we determined all data exclusions, all manipulations, and all measures in the study. Our sample size was predetermined by the number of studies in the Many Labs projects.

## Ethical Approval
This research was approved by the Tilburg University School of Social and Behavioral Sciences Ethical Review Board (nr. TSB_TP_REMA06).

@@

Our unit of analysis is a measure of a single variable within a replication protocol or original article that was used in the main analysis that was replicated. We allowed for multiple variables to be measured per study. We used the replication protocols to identify the measure of each variable. We did not include acquiescence bias checks, manipulation checks, pilot test measures, and measures added for exploratory analyses.

@@

The data on the preregistered replication protocols, and replication datasets from Many Labs 1, 2, 3, & 5 were all retrieved from their respective OSF pages: <https://osf.io/wx7ck/>, <https://osf.io/8cd4r/>, <https://osf.io/ct89g/>, & <https://osf.io/7a6rd/>. Both the replication protocols and replication datasets were scanned through to ensure that the planned analyses were feasible. However, no coding or analysis of either of them had taken place before the analyses were preregistered. Further details on the search strategy can be found in the [coding protocol information file](../../SupplementaryMaterials/CodingProtocols/coding_protocol_information.Rmd) in the supplementary materials.

@@

We extracted reported measurement information from the original articles and replication protocols using our preregistered coding protocol. We extracted the reported reliability coefficient and type of index (Cronbach’s Alpha, retest, interrater, etc.) when present. Similarly, we coded if any psychometric construct validity evidence, such as a factor analysis, was presented for the measure. We additionally included twenty items that were based on the QMP table presented in @flakeMeasurementSchmeasurementQuestionable2020. For each of these items we a piece information we would want to see reported with regards to the measurement was described. If the information was clearly reported we coded the item as true; false if not or not clear enough; or not applicable if not relevant for that measure (e.g., reporting results from a factor analysis for single-item measures). Example items can be seen in Table \@ref(tab:QMPCodingInfoTable).

@@

We initially intended to form a QMP index using these QMP items and perform regression analyses using this index, but this index could not be validated properly and its results would be misleading to present here in the main article. A more detailed explanation of what was omitted and why, as well as the results from these preregistered analyses can be found in [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_exploratory_version_pre-reg_analyses.Rmd).

@@

QMP_data$reliability_reported_org <- ifelse(original_QMP_data$reliability_type != "Not Reported" & original_QMP_data$reliability_type != "" & !is.na(original_QMP_data$reliability_type), TRUE, ifelse(original_QMP_data$reliability_type == "Not Reported", FALSE, NA))

QMP_data$reliability_reported_rep <- ifelse(replication_QMP_data$reliability_type != "Not Reported" & replication_QMP_data$reliability_type != "" & !is.na(replication_QMP_data$reliability_type), TRUE, ifelse(replication_QMP_data$reliability_type == "Not Reported", FALSE, NA))

@@

### Recalculating Data

We calculated reliability for each measure from the replication datasets with suitable data for each lab the measure was used in. We calculated both Cronbach’s alpha, as well as its standard error using formulas 2 & 3 from @duhachekAlphasStandardError2004a. Then we entered these two values into a meta-analysis of the measure's reliability, also commonly referred to as a Reliability Generalization (RG) Meta-Analysis [@botellaManagingHeterogeneityVariance2012; @lopez-ibanezReliabilityGeneralizationMetaanalysis2024; @vacha-haaseReliabilityGeneralizationExploring1998]. Using RG Meta-Analysis we quantified the degree of true variation (or heterogeneity) in reliability coefficients across lab locations. We performed the RG Meta-Analysis using the rma function from the metafor R package [*v`r getNamespaceVersion("metafor")[[1]]`*; @R-metafor] and default settings. We evaluated the heterogeneity using the tau statistic and the Cochran's Q-test [@cochranCombinationEstimatesDifferent1954]. These indicators have received criticism as indicators of heterogeneity, especially when within study sample sizes are small and power to detect heterogeneity is low [@hoaglinMisunderstandingsCochransTest2016; @pereiraCriticalInterpretationCochrans2010]. Therefore, we also present the prediction interval and implore that the heterogeneity results should be viewed critically [@borensteinAvoidingCommonMistakes2024]. We implemented no correction for bias, because the Many Labs replications were not at risk of publication bias.

Our analyses will focus on Cronbach’s Alpha, because it is common in research, which also allows us to make comparisons between calculated and reported reliabilities. Furthermore, we were able to calculate the standard error of alpha to be used in the RG meta-analysis. We additionally estimated McDonald’s Omega for each lab from the same set of replications as for Cronbach's Alpha, since it has been argued to be a more informative measure of reliability than Cronbach's Alpha, while also simultaneously providing some validity evidence [@crutzenScaleQualityAlpha2017b; @dengTestingDifferenceReliability2017]. McDonald’s Omega was calculated using the omega function in the *psych* R package [*v`r getNamespaceVersion("psych")[[1]]`*; @R-psych]. Default arguments were used in the function except the nfactors argument, which was set to 1. No RG Meta-Analysis was performed on McDonald's Omega, as we could not find a formula for calculating its standard error.

@@

Finally, we also tested these measures for unidimensionality. Our unidimensionality check serves a double purpose. First, unidimensionality is one of the assumptions of Cronbach's Alpha. If this assumption does not hold for a measure, our Cronbach's Alpha estimates give a biased estimate of the reliability. Second, all measurement items for which unidimensionality was checked, were used to form a singular index of one latent variable. Certainly, not all singular indexes require the underlying latent factor model to be unidimensional (e.g., general intelligence can be used as a variable on its own or sub-divided in multiple components such as numerical and verbal intelligence). Still, we believe it is not unreasonable to assume that for most of the single index measures we should observe a unidimensional factor model to have at least adequate fit.

We tested for unidimensionality using two tests on the data from each lab for each measure. If at least one of these tests was passed, the measure in that lab was marked as unidimensional. For the first test we fit a Confirmatory Factor Analysis (CFA) model with one factor to the data, and we then evaluate the RMSEA value. If this value is below .08, the test is passed. For the second test we run a parallel analysis. This runs multiple Exploratory Factor Analyses (EFA) where the number of factors in the model is increased by 1 until the number of factors is one less than the number of items. It then compares the eigenvalues (an indication of how much variance is explained by that factor) of each factor to the eigenvalues for that factor if the data matrix was effectively random. If only the first factor has an eigenvalue that is significantly higher than the eigenvalue when the data matrix is random, the test is passed. We chose a combination of these two tests, as the RMSEA is known to be biased for models with small degrees of freedom [@kennyPerformanceRMSEAModels2015], while the parallel analysis may be less suited if a two or more factor solution would also fit the sample item data.

>>>>

classoption       : man
output            : papaja::apa6_docx
knit              : worcs::cite_all
---

```{r setup, include = FALSE}
# loading R libraries
library(papaja)
library(worcs)
library(lavaan)
library(psych)
library(metafor)
library(forcats)
library(ggplot2)
library(grid)
library(patchwork)

@@

\renewcommand{\arraystretch}{0.7}

<!-- reducing the line spacing within tables -->

\renewcommand{\topfraction}{.8}

<!-- max fraction of page for floats at top -->

\renewcommand{\bottomfraction}{.8}

<!-- max fraction of page for floats at bottom -->

\renewcommand{\textfraction}{.15}

<!-- min fraction of page for text -->

\renewcommand{\floatpagefraction}{.8}

<!-- min fraction of page that should have floats .66 -->

@@

The challenge with measurement in quantitative psychological research is that unlike height or weight, psychological constructs cannot be directly measured, as they cannot be directly observed. Instead, we use scores from a measurement as an indicator for a psychological construct. Yet, it cannot simply be assumed that any measure will form a good indicator of the constructs of interest. The measure has to be validated by establishing the reliability and construct validity of the measure. "Reliability refers to the consistency of scale scores when a construct is assessed multiple times or in multiple ways" [@crutzenScaleQualityAlpha2017b; pp. 244]. Meanwhile, construct validity refers to whether the variance in the measured item scores between participants can be attributed to the variance in the unobserved construct(s) of interest between participants [@cronbachConstructValidityPsychological1955; @vazireCredibilityReplicabilityImproving2022].

However, research indicates that measures often lack reliability and construct validity evidence !!!CITE!!!, either because the evidence is not reported, or because the measures are not validated. @flakeMeasurementSchmeasurementQuestionable2020 dubbed these practices - that raise doubts about a measurement’s validity - Questionable Measurement Practices (QMPs), being a term analogous to Questionable Research Practices [QRPs; Simmons et al. (2011); John et al. (2012); Wicherts et al. (2016)]. Existing research has already shown practices that reflect QMPs to be relatively common in both replication and original studies !!!CITE!!!. The purpose of this study is to provide a combined overview of the information on the reporting practices of measurement in replication and original with reliability and construct validity indices obtained from the shared item response data. By combining information on reporting with our own calculated indices, we can reflect on which validity issues lie in reporting and which are an issue with the measurement itself.

@@

One issue that has been observed with respect to measurement validation is that the reported measurement information is typically insufficient for readers to understand, evaluate, and reuse the measurement that was used [!!!CITE]. @flakeConstructValidityValidity2022 documented the measurement reporting practices among 100 replications and their respective original articles from the Reproducibility Project Psychology [@opensciencecollaborationEstimatingReproducibilityPsychological2015]. They coded the number of measures, the content of the measures, and information describing and justifying the measurement. They observed limited reporting of evidence demonstrating the reliability and validity of the measurement. Additionally, only eight of the 40 translated scales contained validity evidence for the translated version. A similar lack of reliability and validity reporting has been observed in other studies as well [@hoganEmpiricalStudyReporting2004; @flakeConstructValidationSocial2017]. If readers cannot glance the construct validity and reliability of a measure from the reported information, then readers lack the basic information needed to determine whether the measured variables are actually related to the constructs of interest. In turn, if we cannot determine whether the constructs of interest are captured in the measured variables or not, then the relation of the results of the statistical analysis using these variables and any psychological phenomena of interest is also strenuous. In short, if the reported information does not show that the measurement was valid, then any substantive conclusions from the data are unfortunately left unsubstantiated.

Further findings by @flakeConstructValidityValidity2022 and others [@flakeConstructValidationSocial2017; @maireadshawMeasurementPracticesLargescale2020] show that measurement reporting was not only limited in terms of the reliability and validity evidence needed to evaluate the measure. The lack of information was also observed for basic content descriptions such as the number of items, the response format, and the scoring of the scale were irregular. This creates challenges for future researchers that want to reuse to measurement. Specifically for replication studies attempting to reconstruct the measurement from these incomplete descriptions, they may end up with a measurement that assesses the constructs in a substantially different way from the original study, or even assess different constructs altogether. If different constructs are assessed, the replication cannot be seen as a test of the same phenomenon as the original. If the same constructs are assessed, but in a substantially different way, the estimated effects in the replication cannot easily be put side-by-side with the effects in the original study. In either case, substantial comparisons between original and replication are hindered. The inability to reuse a measure does not only affect replications however, it also limits our ability to validate the measure thoroughly. Even if the measure is shown to be construct valid in one context, the factor relations may not be stable for this measure in other contexts and implementations, a concept known as measurement invariance [@hornPracticalTheoreticalGuide1992; @cheungDirectComparisonApproach2012]. While it is important to assess measurement (in)variance before using measures in a new context, if that measure is not reusable, the invariance cannot even be assessed.

Our first aim is to extend these existing findings on measurement reporting practices with a descriptive account of these practices for the Many Labs replications and the related original studies. We evaluate to what extent the reporting and use of item-based measurement scales in our sample allows us to evaluate and reuse the measurement. We do not ourselves evaluate whether the reported measurement information provide sufficient justification for its use, merely that information is reported such that that part of the measurement can be evaluated. We extend earlier investigations through new questions about the presence of justification for measurement selection or creation, item transformations such as reverse coding being described, the administration format being described, a change in the number of items from the source, whether changes in items response options, or number of items, or administration were validated or justified. All of our measurement reporting items were inspired by and categorized based on the QMP table in @flakeMeasurementSchmeasurementQuestionable2020.

We chose the Many Labs replications and associated original studies as our sample, due to them being of particular interest. The Many Labs replications were a series of large-scale collaborations in which multiple labs across the world directly replicated classic and contemporary psychological studies [@kleinInvestigatingVariationReplicability2014a; @ebersoleManyLabs32016; @kleinManyLabs22018b; @ebersoleManyLabs52020d; @kleinManyLabs42022]. The original studies chosen for replication in the Many Labs were not only picked based on ease and feasibility, but importantly for us they were also picked to display a diverse range of effects that were also of key interest to the field. This makes these studies an important sample to evaluate, because the replicated effects represent a broad range of relevant findings. Furthermore, because the Many Labs projects used preregistered and documented structured protocols, we expect the measurement reporting for the replications to represent a high standard within the field. Any issues in measurement reporting here might suggest that other replications could face similar or greater challenges.

## Reliability

Psychometrics offers various ways in which to assess construct validity and reliability [@nunnallyOverviewPsychologicalMeasurement1978; @mellenberghConceptualIntroductionPsychometrics2011]. It is often the results from these psychometric analyses that form one of the pre-requisite pieces of evidence for assessing whether or not the measure is valid or not.

When psychometric indicators are reported - which as mentioned earlier is not common - it is often limited to Cronbach's Alpha, a commonly used indicator for reliability. Cronbach's Alpha comes with strong assumptions that are themselves rarely tested [@crutzenScaleQualityAlpha2017b]. Furthermore, research by @husseyAberrantAbundanceCronbachs2023 has shown evidence that the reporting of reliability may not only be little, but also biased. They observed a disproportional amount of Cronbach's Alpha values at the common acceptably reliable threshold value of .70, and relatively low reporting below .70. Thus, the lack of reported measurement evidence may on occasion be hiding psychometric skeletons in the closet.

As a result, if we want to evaluate the reliability of measurement in our sample, we cannot rely on the reported information alone to give us a representative picture. Thus, we evaluate the measurement reliability within the Many Labs original and replication studies by estimating it from the item response data. The data on the item responses are openly available per lab for our sample. As a result, we can evaluate not only the reliability per measure, but also the variation in reliability across labs. The variation is relevant because Cronbach's alpha is an indicator of reliability within a particular sample and not of the reliability of the measure in general, as it is proportional to the total variance in the target variable in the sample. Despite this many researchers report and interpret Cronbach's Alpha as a universal quality of the measure [@cortinaWhatCoefficientAlpha1993; @schmittUsesAbusesCoefficient1996]. @maireadshawMeasurementPracticesLargescale2020 has so far observed that for Many Labs 2 the overall sample Cronbach's alpha level across scales was below .5, a degree of reliability far below what many would consider acceptable for most research purposes. It is our second aim to empirically evaluate both the degree as well as the variation of reliability of the measures in our sample that includes the other Many Labs projects.

## Unidimensionality

Reliability is a pre-requisite to construct validity, because a measure for which a participant’s response is not consistent, cannot capture a stable construct [Kaplan and Saccuzzo (2013, pp. 154–155)]. Another, important pre-requisite for many measures is unidimensionality. Unidimensionality means that the items on a measure assess, show evidence of measuring a single construct. Thus, if a set of items are intended to measure the same one construct, then unidimensionality is key to the construct validity of that set of items. Additionally, most reliability indicators - including Cronbach's Alpha - cannot be assessed without first making sure that the measure is unidimensional. Thus for our third aim we again used the item response data. This time hitting two birds with one stone. We check the measures' construct validity, and we check if one of the key assumptions of Cronbach's Alpha is met.

!!!substantively belangrijk, want de scores worden als unidimensioneel geinterpreteerd. Alpha assumptie testen, als kleiner deel bespreken; Reliability kan in sommige gevallen slecht zijn als de schaal gewoon multi-dimensioneel is. Eerst een beetje techniek, daarna meer kwalitatief oordeel dat het gewoon belangrijk is voor interpretatie!!!

@maireadshawMeasurementPracticesLargescale2020 checked the factor structure on the openly available item data from Many Labs 2 [@kleinManyLabs22018b]. They observed that no scales in their sample did the results from the factor analysis meet all of their evaluation criteria for unidimensionality. @maireadshawMeasurementPracticesLargescale2020 had access to measures that were used across multiple contexts to evaluate their validity across more than one instance. However, in practice, measures are frequently made on the fly and reused maybe once or never [@weidmanJingleJangleEmotion2017; @elsonPsychologicalMeasuresArent2023; @anvariFragmentedFieldConstruct2025; @anvariDefragmentingPsychology2025]. This is dangerous, because these measures are often not validated before use, and if they cannot be reused, they are not going to be validated afterwards either. Furthermore, validating a scale requires substantial sample sizes in most cases [@maccallumSampleSizeFactor1999, @gorsuchFactorAnalysis2013], sample sizes that many original studies cannot obtain, in which case these measures are reliant on future research to obtain the required sample size to validate the measure.

Thus, for our third research aim - similarly to our aim with reliability - we check the unidimensionality of measures from the Many Labs projects per lab with meta-analytic assessment of the variation in unidimensionality across labs. The combined goal of our three research aims is to create a description of the measurement use in our data.

@@

## Preregistration

We preregistered data collection, coding protocol, and planned analyses: <https://osf.io/jgxyu>. We deviated from our coding protocol as is explained further in the text. Our pre-registered analyses have been move to the [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_exploratory_version_pre-reg_analyses.Rmd) in favor of focusing on the descriptive results here.

## Data, Materials, and Online Resources

This manuscript was created in RStudio [*v`r rstudioapi::versionInfo()$version`*; @R-Rstudio] with R Version `r paste0(R.Version()$major, ".", R.Version()$minor)` [@R-base], and generated using the Workflow for Open Reproducible Code in Science [*v`r getNamespaceVersion("worcs")[[1]]`*; @R-worcs] to ensure reproducibility and transparency. All code and data used to generate this manuscript and its results are available at: <https://github.com/CasGoos/measurement_and_replication> and <https://osf.io/9r8yt/> (DOI: 10.17605/OSF.IO/9R8YT).

## Reporting

We report how we determined all data exclusions, all manipulations, and all measures in the study. Our sample size was predetermined by the number of studies in the Many Labs projects.

## Ethical Approval

This research was approved by the Tilburg University School of Social and Behavioral Sciences Ethical Review Board (nr. TSB_TP_REMA06).

@@

Our unit of analysis is a measure of a single variable within a replication protocol or original article that was used in the main analysis that was replicated. For example, if conscientiousness and agreeableness were both measured using a big-five personality questionnaire, each of which was a variable in a replicated effect, then both the conscientiousness and agreeableness part of that questionnaire would be coded as their own unit of analysis. We also allowed for multiple variables to be measured per study. We used the replication protocols to identify the measure of each variable. We did not include acquiescence bias checks, manipulation checks, pilot test measures, and measures added for exploratory analyses. Our final sample size was `r nrow(coded_data_replications)` measures of unique variables for both original and replication studies\^[Initially the original articles contained 3 more measures of unique variables than the replication protocols. This difference was due to the way that the moral foundations questionnaire was framed in the original article compared to in the replication protocol. In the original article it was framed as measuring five different moral foundations, while in the replication protocol the measure assessed the two overarching categories that were used to test the main effect in both the original and replication research. The measurement information reported was comparable across all five categories, and thus it was deemed that the measurement could be reduced to reflect two overarching categories facilitate easier comparison between measurement in original and replication.]

@@

The data on the preregistered replication protocols, and replication datasets from Many Labs 1, 2, 3, & 5 were all retrieved from their respective OSF pages: <https://osf.io/wx7ck/>, <https://osf.io/8cd4r/>, <https://osf.io/ct89g/>, & <https://osf.io/7a6rd/>. Both the replication protocols and replication datasets were scanned through to ensure that they were the correct files to code measurement reporting information from. However, no coding or analysis of either of them had taken place before the analyses were preregistered. Further details on the search strategy can be found in the [coding protocol information file](../../SupplementaryMaterials/CodingProtocols/coding_protocol_information.Rmd) in the supplementary materials.

@@

We extracted reported measurement information from the original articles and replication protocols using our preregistered coding protocol. We extracted the reported reliability coefficient and type of index (Cronbach’s Alpha, retest, interrater, etc.) when present. Similarly, we coded if any psychometric construct validity evidence, such as a factor analysis, was presented for the measure. We additionally included twenty items that were based on the QMP table presented in @flakeMeasurementSchmeasurementQuestionable2020. For each of these items we checked if a piece information we would want to see reported with regards to the measurement was described. If the information was clearly reported we coded the item as true; false if not or not clear enough; or not applicable if not relevant for that measure (e.g., reporting results from a factor analysis for single-item measures). Example items can be seen in Table \@ref(tab:QMPCodingInfoTable).

@@

We initially intended to construct a QMP index from the QMP items and perform regression analyses between this index and replication outcomes. However, this index could not be validated properly and its results would be misleading to present here in the main article. A more detailed explanation of what was omitted and why, as well as the results from these preregistered analyses can be found in [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_exploratory_version_pre-reg_analyses.Rmd).

@@

QMP_data$reliability_reported_org <- ifelse(coded_data_original$N_items == "multiple item measure", ifelse(original_QMP_data$reliability_type != "Not Reported" & original_QMP_data$reliability_type != "" & !is.na(original_QMP_data$reliability_type), TRUE, ifelse(original_QMP_data$reliability_type == "Not Reported", FALSE, NA)), NA)

QMP_data$reliability_reported_rep <- ifelse(coded_data_replications$N_items == "multiple item measure", ifelse(replication_QMP_data$reliability_type != "Not Reported" & replication_QMP_data$reliability_type != "" & !is.na(replication_QMP_data$reliability_type), TRUE, ifelse(replication_QMP_data$reliability_type == "Not Reported", FALSE, NA)), NA)

@@

### Calculating Reliaiblity

We calculated reliability for each measure from the replication datasets with suitable data for each lab the measure was used in. We calculated both Cronbach’s alpha, as well as its standard error using formulas 2 & 3 from @duhachekAlphasStandardError2004a. We used these values to conduct a meta-analysis of the measure's reliability, also commonly referred to as a Reliability Generalization (RG) Meta-Analysis [@botellaManagingHeterogeneityVariance2012; @lopez-ibanezReliabilityGeneralizationMetaanalysis2024; @vacha-haaseReliabilityGeneralizationExploring1998]. We performed the RG Meta-Analysis using the rma function from the metafor R package [*v`r getNamespaceVersion("metafor")[[1]]`*; @R-metafor] and default settings. We then used the results from the meta-analysis to evaluate the heterogeneity via the tau statistic and the Cochran's Q-test [@cochranCombinationEstimatesDifferent1954]. These indicators have received criticism as indicators of heterogeneity, especially when within study sample sizes are small and power to detect heterogeneity is low [@hoaglinMisunderstandingsCochransTest2016; @pereiraCriticalInterpretationCochrans2010]. Therefore, we also present the prediction interval and implore that the heterogeneity results should be viewed critically [@borensteinAvoidingCommonMistakes2024]. We implemented no correction for bias, because the Many Labs replications were not at risk of publication bias.

Our analyses will focus on Cronbach’s Alpha, because it is common in research, which also allows us to make comparisons between calculated and reported reliabilities. Furthermore, we were able to calculate the standard error of alpha to be used in the RG meta-analysis. However, Cronbach's Alpha comes with strong assumptions on the underlying factor structure, including that the measure is unidimensional, which means that there should a single factor underlying the measurement scores. Therefore, we also estimated McDonald’s Omega for each lab from the same set of replications as for Cronbach's Alpha, since it has been argued to be a more informative measure of reliability than Cronbach's Alpha with less strict assumptions [@crutzenScaleQualityAlpha2017b; @dengTestingDifferenceReliability2017]. The results based on Omega can be found in [Supplementary Analyses D](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_omega_analyses.Rmd).

@@

### Unidimensionality

All measurement items for which we checked unidimensionality, were used to form a singular index of one latent variable. Therefore, unidimensionality presents a valuable indication of the construct validity of a measure in our dataset. To test for unidimensionality, we fit a single-factor model on the item response data of each individual lab with the relevant measurement data. This was done to simulate the inference a lab would make if they were to check for unidimensionality. Our inference of unidimensionality is based on a set of five model fit indices. If the indices point towards a good unidimensional fit that is also consistent across labs - as we also evaluate the variability across labs - then we can say that with this preliminary evidence at least, we did not observe any issues with the construct validity of that measure. If the indices point towards a lack of unidimensionality in a substantial number of labs, that would be a warning sign for the lack of construct validity for that measure. Our goal is not to fully check the validity of these measures, this requires additional steps that are beyond the scope of this study.

For the first four of our five fit indices we fit a Confirmatory Factor Analysis (CFA) model with one factor to the data, and we then evaluate the RMSEA value, CFI value, SRMR value, and the result from the exact fit test. For the RMSEA and SRMR value we checked if it was below .08. For the CFI value we checked if the value was above .90. Finally, for the exact fit test we evaluated if the fit test was statistically significant at an alpha of .05. These values are based on common thresholds used to determine adequate fit. We consider the use of these thresholds sufficient for our descriptive aim, even though we understand apprehension against rules of thumb when used to evaluate measurement in individual studies.

For the final index we ran a parallel analysis. A parallel analysis runs multiple Exploratory Factor Analyses where the number of factors in the model is increased by 1 until the number of factors is one less than the number of items. It then compares the eigenvalues (an indication of how much variance is explained by that factor) of each factor to the eigenvalues for that factor if the data matrix was effectively random. If only the first factor has an eigenvalue that is significantly higher than the eigenvalue when the data matrix is random, the test is passed. We chose a combination of indices since each one has their own limitations, and combining them gives us a more robust picture of the unidimensionality of the measures.
